---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

### tidystm: Extract (tidy) effect from `estimateEffect` in the `stm` package

[![Travis-CI Build Status](https://travis-ci.org/.svg?branch=master)](https://travis-ci.org/)

Extracts the effect of a covariate on a set of topics selected by the user. Different effect types available depending on type of covariate. Before running this, the user should run a function to simulate necessary confidence intervals. See estimateEffect of the stm package.

#### Install

You need the `devtools` package in order to install `tidystm`. You can install it using the follow code (note that you only need to run this once):

```{r}
if (!require(devtools)) install.packages("devtools")
```

You can then install `tidystm` by running:

```{r, eval = FALSE}
devtools::install_github("mikaelpoul/tidystm", dependencies = TRUE)
```

#### Use

The package, for now, includes one function: `extract.estimateEffect()`. You run it just as you would run the `plot.estimateEffect()` function included in the `stm` package. E.g.:

```{r}
## Load the packages
library(stm)
library(tidystm)

## Load the example data from the stm pacakge
data(gadarian)

## Estimate the effect on all three topics and return the point
## estimates in a tidy data frame
prep <- estimateEffect(1:3 ~ treatment, gadarianFit, gadarian)
effect <- extract.estimateEffect(prep, "treatment", model = gadarianFit, method = "pointestimate")

print(effect)
```
